Detection of DCIS and IDC in Whole-Slide\\ H\&E Stained Breast Histopathology Images Using Stacked Convolutional Neural Networks

### 2016-10-05 tex/article.tex
Add augment example figure, increase LR
Add section on parameters

@@

\subsubsection{HSV jittering}
HSV is a colorspace that represents a color image in three channels; a \emph{hue} (color), \emph{saturation} (vibrance) and a \emph{value} (brightness) channel. There exists a large variability in the staining of the slides, which shows itself mostly in the hue and saturation channel. We randomly jitter the hue and saturation of an image with a random value between -0.075 and 0.075. The values of all pixels are then clipped between 0 and 1.

>>>>

\subsection{Model parameters}
A starting learning rate of 0.05 was used for the WRN-4-2 model, 0.01 for VGG-16. These values were emperically determined to work well. Rectified linear units were used throughout both networks as nonlinearities. A minibatch size of 22 was used per parameter update step, for determining the performance on the validation set batches of 128 patches were used. Every patch is labeled with the value of the center pixel in the annotations.

To create one minibatch first the classes are sampled with uniform probability. Then for every class random locations are chosen within the annotation with this class. As this allows for near-infinite amount of locations where this sampling can take place, the concept of epoch is somewhat lost. We will define one epoch to be 300 minibatches for training, and 200 for validation.

@@

\subsubsection{HSV jittering}
HSV is a colorspace that represents a color image in three channels; a \emph{hue} (color), \emph{saturation} (vibrance) and a \emph{value} (brightness) channel. There exists a large variability in the staining of the slides, which shows itself mostly in the hue and saturation channel. We randomly jitter the hue and saturation of an image by multiplying it with a random value between -1.075 and 1.075. The values of all pixels are then clipped between 0 and 1.

\begin{figure}[!t]
\centering{}
\includegraphics[width=3.4in]{augment_examples}
\caption{Examples of augmentations applied to patches of 224 by 224 pixels. In the left column the original image is shown, in the other columns augmented versions of this same image are shown. Note the slight shift in hue and saturation for some of the augmentations.}
\label{fig_augment}
\end{figure}
